---
title: "M4metalearning Framework"
output:
  pdf_document: default 
  html_notebook: default
---


#### choosing subset of M4 ts (there is 100_000 ts in the dataset)
```{r}
library(M4metalearning)
library(M4comp2018)
set.seed(31-05-2018)
indices <- sample(length(M4))

M4_train <- M4[ indices[1:15]]
M4_test <- M4[indices[16:25]]
M4_train <- temp_holdout(M4_train)
M4_test <- temp_holdout(M4_test)
```

#### typical time series

```{r}

print(M4[[1]]$x)
plot(M4[[1]]$x)
```

#### temp_holdout method

```{r}
print(temp_holdout(M4[1])[[1]]$x)
```


```{r}
print(temp_holdout(M4[1])[[1]]$xx)
```


#### Making forecast and calculating errors for metaalgorithm training

```{r}
M4_train <- calc_forecasts(M4_train, forec_methods(), n.cores=3)
M4_train <- calc_errors(M4_train)
```


#### features for metaalgorithm aka ts-classifier

```{r}
library(tsfeatures)
M4_train <- THA_features(M4_train)

```

```{r}
train_data <- create_feat_classif_problem(M4_train)
```
```{r}
head(train_data$data)
```

#### training metalearner classifier for minimise error of ensemble on test period

```{r}
meta_model <- train_selection_ensemble(train_data$data, train_data$errors)
```
##### test dataset forecasts
```{r}
M4_test <- calc_forecasts(M4_test, forec_methods(), n.cores=1)
```

##### features to predict weights
```{r}
M4_test <- THA_features(M4_test, n.cores=1)
```


```{r}
test_data <- create_feat_classif_problem(M4_test)
```

#### predictions of weights for every ts and forecast method:
```{r}
preds <- predict_selection_ensemble(meta_model, test_data$data)
```
```{r}
preds
```

#### forecasting
```{r}
M4_test <- ensemble_forecast(preds, M4_test)

```
```{r}
print(M4_test[[1]]$xx)
print(M4_test[[1]]$y_hat)
```


    